### 2024-10-07 writing/manuscript.Rmd
specify longtable and lavaan versions

---
bibliography: citations.bib
csl: nature.csl
header-includes:
- \usepackage[left]{lineno}
- \usepackage{ragged2e}
- \usepackage{caption}
- \usepackage{longtable}
- \usepackage[labelformat = empty]{caption}
- \usepackage{afterpage}
- \usepackage{fontenc}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage[symbol]{footmisc}
- \usepackage{numprint}
- \usepackage{lineno}
- \npthousandsep{,}
- \definecolor{bleu}{HTML}{2200cc}
- \renewcommand{\thefootnote}{\fnsymbol{footnote}}
notes-after-punctuation: no
urlcolor: bleu
linkcolor: bleu
output:
  pdf_document: default
editor_options:
  markdown:
    wrap: sentence
---

@@

```{r load_libraries_and_functions}
# if manuscript not knitting run this code separately, and make sure all packages are installing correctly
library(pacman)
p_load(
  BayesFactor,
  broom,
  broom.mixed,
  cowplot,
  effectsize,
  gamlss,
  ggpubr,
  heplots,
  here,
  janitor,
  kableExtra,
  knitr,
  lavaan,
  partykit,
  png,
  psych,
  semPlot,
  tidyverse
)

>>>>

---
bibliography: citations.bib
csl: nature.csl
header-includes:
- \usepackage[left]{lineno}
- \usepackage{ragged2e}
- \usepackage{caption}
- \usepackage{longtable}[=v4.13]
- \usepackage[labelformat = empty]{caption}
- \usepackage{afterpage}
- \usepackage{fontenc}
- \usepackage{soul}
- \usepackage{xcolor}
- \usepackage[symbol]{footmisc}
- \usepackage{numprint}
- \usepackage{lineno}
- \npthousandsep{,}
- \definecolor{bleu}{HTML}{2200cc}
- \renewcommand{\thefootnote}{\fnsymbol{footnote}}
notes-after-punctuation: no
urlcolor: bleu
linkcolor: bleu
output:
  pdf_document: default
editor_options:
  markdown:
    wrap: sentence
---

@@

```{r load_libraries_and_functions}
# if manuscript not knitting run this code separately, and make sure all packages are installing correctly
library(pacman)
p_load(
  BayesFactor,
  broom,
  broom.mixed,
  cowplot,
  effectsize,
  gamlss,
  ggpubr,
  heplots,
  here,
  janitor,
  kableExtra,
  knitr,
  lavaan, # this script was written using lavaan version 0.6-17, available at: https://cran.r-project.org/src/contrib/Archive/lavaan/
  partykit,
  png,
  psych,
  semPlot,
  tidyverse
)
